An alternative MIP formulation for the Military Flight and Maintenance Planning problem

### 2019-11-20 latex/ROADEF2020/article.tex
changes to ROADEF2020.

\author{Franco Peschiera\inst{1}, Alain Ha{\"i}t\inst{1}, Olga Batta{\"i}a\inst{1}, Nicolas Dupin\inst{2}}

\institute{
ISAE-SUPAERO, Universit{\'e} de Toulouse, France \\
\email{\{franco.peschiera,alain.hait,olga.battaia\}@isae-supaero.fr}\\
Laboratoire de Recherche en Informatique, France \\
\email{dupin@lri.fr}

}

@@

    The problem consists in assigning military aircraft $i \in \mathcal{I}$ to a given set $j \in \mathcal{J}$ of missions while scheduling the check over a time horizon divided into $t \in \mathcal{T}$ periods. Missions have known start and end dates, each requires $R_j$ aircraft to be assigned at any given time and to fly $H^\prime_{jtt'}$ when assigned between periods $t$ and $t'$. Each aircraft $i$ can be assigned to only missions $j \in \mathcal{JI}_i$ and is assumed to fly $U^{\prime}_{tt'}$ hours between periods $t$ and $t'$. Each period $t$ has $j \in \mathcal{JT}_t$ active missions.

    Each aircraft $i$ needs a check every $H^{max}$ flight hours or less and has $Rft^{Init}_i$ remaining flight hours at the beginning of the planning horizon. Each aircraft can be assigned its first check during periods $t \in \mathcal{T}^{M_{Init}}_i$ and, if assigned a first check in period $t$, it can have its second check during periods $t \in \mathcal{T}^{M+}_{t}$. $\mathcal{TTT}_t$ is the set of check patterns that make an aircraft be in maintenance in period $t$; $\mathcal{TTJ}_{jt}$ is the set of mission $j$ patterns that make aircraft be in mission in period $t$; $\mathcal{JTT}_{itt'}$ is the set of mission patterns for aircraft $i$ between periods $t$ and $t'$.

>>>>

\author{Franco Peschiera\inst{1}, Alain Ha{\"i}t\inst{1}, Olga Batta{\"i}a\inst{2}, Nicolas Dupin\inst{3}}

\institute{
ISAE-SUPAERO, Universit{\'e} de Toulouse, France \\
\email{\{franco.peschiera,alain.hait\}@isae-supaero.fr}\\
KEDGE Business School, France \\
\email{olga.battaia@kedgebs.com} \\
Laboratoire de Recherche en Informatique, France \\
\email{dupin@lri.fr}
}

@@

    The problem consists in assigning aircraft $i \in \mathcal{I}$ to a set $j \in \mathcal{J}$ of missions while scheduling checks over a time horizon divided into $t \in \mathcal{T}$ periods. Missions have known start and end dates; and requires $R_j$ aircraft to fly $H^\prime_{jtt'}$ when assigned between periods $t$ and $t'$. Each aircraft $i$ can be assigned to only missions $j \in \mathcal{JI}_i$ and is assumed to fly $U^{\prime}_{tt'}$ hours between periods $t$ and $t'$. Each period $t$ has $j \in \mathcal{JT}_t$ active missions.

    Each aircraft $i$ needs a check after $H^{max}$ flight hours or less; has $Rft^{Init}_i$ remaining flight hours at the beginning of the planning horizon; can be assigned its first check during periods $t \in \mathcal{T}^{M_{Init}}_i$ and, if assigned a first check in period $t$, it can have its second check during periods $t \in \mathcal{T}^{M+}_{t}$. $\mathcal{TTT}_t$ is the set of check patterns that make an aircraft be in maintenance in period $t$; $\mathcal{TTJ}_{jt}$ is the set of mission $j$ patterns that make aircraft be in mission in period $t$; $\mathcal{JTT}_{itt'}$ is the set of mission patterns for aircraft $i$ between periods $t$ and $t'$.
